timesliced_random_cell_selection

### 2018-12-21 src/testing_point_generation.Rmd
repair 2...

```{r}
backna <- sum(!complete.cases(background_all)) #this just counts the number of rows that contain NA values
backna
background_all <- background_all[complete.cases(background_all), ] #removes NA values
backna2 <- sum(!complete.cases(background_all)) #this just counts the number of rows that contain NA values
backna2
write.csv(background_all, "../output/bio/background_point_na_removal_nona", row.names = FALSE)
head(testbackground_all)
```

```{r}
testbackground_all <- subset(testbackground_all, select = -c(temp_depth, temp_surface, salinity_depth, salinity_surface, o2_depth, o2_surface, chl_depth, chl_surface, ssh_surface, mlp_surface))
head(testbackground_all)
```
```{r}
testbackground_all <- subset(testbackground_all, select = -c(longitude_.1, latitude_m.1, optional))
head(testbackground_all)
```

>>>>

```{r}
testbackground_all <- read.csv("../output/bio/background_point_na_removal.csv", header = TRUE)
backna <- count(rowSums(!is.na(testbackground_all)))
backna <- sum(!complete.cases(testbackground_all)) #this just counts the number of rows that contain NA values
backna
testbackground_all <- testbackground_all[complete.cases(testbackground_all), ] #removes NA values
backna2 <- sum(complete.cases(testbackground_all)) #this just counts the number of rows that contain NA values
backna2
write.csv(testbackground_all, "../output/bio/background_point_na_removal_nona.csv", row.names = FALSE)
head(testbackground_all)
```

```{r}
testbackground_all <- subset(testbackground_all, select = -c(temp_depth, salinity_depth, o2_depth, chl_depth))
head(testbackground_all)
```
```{r}
testbackground_all <- subset(testbackground_all, select = -c(longitude_.1, latitude_m.1, optional, optional.1))
head(testbackground_all)
```

### 2018-12-21 src/timesliced_random_cell_selection.Rmd
repair 2...

```{r}
filenames  <- list.files(path = rand_folder, pattern="*.csv", full.names = TRUE) 
background_all <- rbindlist(lapply(filenames,fread, fill = TRUE))
write.csv(background_all, "../output/bio/background_all.csv", row.names = FALSE)
head(background_all)
```

@@

```{r}
background_all$bottom_depth <- get.depth(bat, background_all[ ,8:9], locator = FALSE)
background_all$bottom_depth <- background_all$bottom_depth[, 3] #this step is because get.bath actually produces it's own dataframe with long, lat, and depth. This is extracting the depth column and deplacing data_aea$bottom_depth with the correct data.
write.csv(background_all,"../output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname_bath.csv", row.names = FALSE)
head(background_all$bottom_depth)
```

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete_2007.csv", row.names = FALSE)
background_all <- as.data.frame(background_all_sp)
head(background_all_sp)
```

@@

remove all na values

```{r}
backna <- sum(!complete.cases(background_all)) #this just counts the number of rows that contain NA values
backna
background_all <- background_all[complete.cases(background_all), ] #removes NA values
backna2 <- sum(!complete.cases(background_all)) #this just counts the number of rows that contain NA values
backna2
write.csv(background_all, "../output/bio/background_complete_na.csv", row.names = FALSE)
```

>>>>

```{r}
rand_folder <- "../output/bio/background/rand10kreboot/"      # path to folder that holds multiple .csv files
filenames  <- list.files(path = rand_folder, pattern="*.csv", full.names = TRUE) 
background_all <- rbindlist(lapply(filenames,fread, fill = TRUE))
write.csv(background_all, "../output/bio/background_all.csv", row.names = FALSE)
head(background_all)
```

@@

```{r}
background_all <- read.csv("../output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname.csv", header = TRUE)
background_all$bottom_depth <- get.depth(bat, background_all[ ,8:9], locator = FALSE)
background_all$bottom_depth <- background_all$bottom_depth[, 3] #this step is because get.bath actually produces it's own dataframe with long, lat, and depth. This is extracting the depth column and deplacing data_aea$bottom_depth with the correct data.
write.csv(background_all,"../output/bio/background_all_lonlat_nafo2_sciname_amo_nao_depthname_bath.csv", row.names = FALSE)
head(background_all)
```

@@

    }
}
write.csv(background_all_sp, "../output/bio/background_complete_2007.csv", row.names = FALSE)
background_all2 <- as.data.frame(background_all_sp)
head(background_all_sp)
```

@@

remove all na values THIS CAN BE EDITED TO DOUBLE CHECK FOR NA VALUES

```{r}
backna <- sum(!complete.cases(background_all2)) #this just counts the number of rows that contain NA values
backna
background_all2 <- background_all2[complete.cases(background_all2), ] #removes NA values
backna2 <- sum(!complete.cases(background_all)) #this just counts the number of rows that contain NA values
backna2
write.csv(background_all, "../output/bio/background_complete_na.csv", row.names = FALSE)
```
